Something about lineage metrics

### 2018-03-28 paper.tex
Update on Overleaf.

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment! 
A lineage describes a continuous line of descent, linking ancestors and their descendants. A complete lineage can provide a post-hoc, step-by-step guide to the evolution of an extant organism where each step involves replication and inherited variation. Indeed, lineage analyses are a powerful tool for disentangling the evolution of complexity in both natural and digital systems; digital systems, however, allow for fine-grained lineage tracking at

>>>>

% @AML: Currently taking a crack at this bit of the intro (introducing lineages, etc) on paper at the moment! 
A lineage describes a continuous line of descent, linking ancestors and their descendants. A complete lineage can provide a post-hoc, step-by-step guide to the evolution of an extant organism where each step involves replication and inherited variation. Indeed, lineage analyses are a powerful tool for disentangling the evolution of complexity in both natural and digital systems; digital systems, however, allow for fine-grained lineage tracking at resolutions that are impossible in modern web lab experiments, allowing us to replay the tape of life in exacting detail to tease apart the evolutionary recipe for whatever complex feature we happen to be interested in. 
% Yet, tracking the full details of a single lineage, much less a population of lineages, can be computational expense
